### 2025-07-31 Revision/response.tex

Section 4.2.3:
%\textcolor{blue}{"To investigate the impact of different server configurations on the performance of the algorithms, we conduct additional experiments on a server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset, and the results are shown in Figure 12b. Compared with the experimental results on the original server, the relative ranking of the algorithms remains largely unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations. Due to the lower CPU frequency and smaller RAM capacity, the QPS values are slightly lower across all methods."}
\textcolor{blue}{"To investigate the impact of different server configurations on the performance of the algorithms, we conduct additional experiments on an Ubuntu 20.04 server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz featuring 128GB of RAM and 84 MiB of L3 cache using the YT-Audio-Real dataset, and the results are shown in Figure 10. It is not difficult to see that the relative ranking of the algorithms under the two servers essentially remains unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations. Due to the lower CPU frequency, reduced RAM capacity, and smaller L3 cache, all methods demonstrate slightly lower QPS values."}

Section 4.3.3:
\textcolor{blue}{"Consistent with Section 4.2.3, we conduct range filtering experiments on the YT-Audio-Real dataset using two server configurations, with results presented in Figure 15. Although the third-ranked algorithm differs, we consider the ranking order remains stable since the performance of the third and fourth algorithms is comparable. Therefore, different server configurations only affect the performance of individual algorithms, with minimal impact on their relative performance ranking."}

\begin{figure}[htbp]
	\centering
	\includegraphics[width=0.48\textwidth]{fig/attribute_legend.pdf}
	\includegraphics[width=0.495\linewidth]{fig/attribute_85.pdf}
	\includegraphics[width=0.47\linewidth]{fig/attribute_71.pdf}
	\caption{Different Platforms (AF)}
	\label{fig:attribute-cross-platform}
\end{figure}

\begin{figure}[htbp]
	\centering
	\includegraphics[width=0.48\textwidth]{fig/range_legend.pdf}
	\includegraphics[width=0.495\linewidth]{fig/range_85.pdf}
	\includegraphics[width=0.47\linewidth]{fig/range_71.pdf}
	\caption{Different Platforms (RF)}
	\label{fig:range-cross-platform}
\end{figure}

@@

Section 4.2.3:\textcolor{blue}{"As shown in the figure 11, on the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating good adaptability to large-scale datasets. However, this also comes with significant memory overhead. The clustering-based algorithm Faiss+HQI\_Batch shows moderate performance but has very low memory overhead, which also has certain practical significance. Furthermore, we do not present the results of StitchedVamana and CAPS, as their recall remained consistently low. StitchedVamana sets the search entry point to 0 by default, which makes it prone to getting stuck in local optima when the entry is far from the target region, hindering effective navigation. CAPS, on the other hand, cannot properly run large-scale dataset experiments because its code implementation does not account for such scenarios."}

Section 4.3.3:
\textcolor{blue}{"As shown in the figure 16, On the deep100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged. However, their high performance is achieved at the cost of extremely high memory consumption, as detailed in Figure 12d. Meanwhile, VBASE and Faiss demonstrate moderate performance but significantly lower memory consumption than the top 3 algorithms."}

%%%%%%%%%%%%%%%%%%%%%% R9 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{metarevision}
		\textit{Clearer insights and guidelines wrt the strength and weaknesses of the compared system.}
	\end{metarevision}
}

\noindent
\textbf{Response:} 
%Thank you for your valuable suggestion. We agree that our previous analysis of the strengths and weaknesses of the algorithms was not sufficiently clear.
%
%To address this, we add a summary table that provides a clearer and more structured comparison of the strengths and weaknesses of each algorithm, offering deeper insights and more concrete guidelines for understanding their trade-offs.
Thank you very much for your insightful comments. We fully agree with your views. We have revised the discussion section of the paper accordingly. In this section, we have added a recommendation table for the algorithms, which summarizes their performance under various conditions. Additionally, we have provided a more in-depth analysis of the internal mechanisms of each algorithm in the text, aiming to uncover the fundamental reasons behind their performance.
\textbf{(Please see Section 5.1.1, Section 5.1.2 and Section 5.1.3, highlighted in blue in the revised manuscript.)}

### 2025-07-31 Revision/response.tex

%For range filtering, please see section 4.3.1.
 %\textbf{(Please refer to the blue highlighted parts in Section 4.3.1 for range filtering.)}
 Section 4.3.1:
\textcolor{blue}{\textit{\textbf{"Peak memory.}}  
	As explained in the attribute filtering analysis, methods with larger index sizes (including the dataset) tend to exhibit higher peak memory consumption. As shown in Figure12c and Figure12d, range filtering also adheres to this pattern.}

	\textcolor{blue}{WinFilter also presents an exception:  its peak memory usage is also affected by the level of parallelism. Although the final index size remains relatively small, the peak memory usage increases significantly during both construction and search. During construction, this is caused by the parallel building of local indices for each tree node, which results in substantial temporary memory usage. Similarly, during search, WinFilter needs to load multiple local indices in parallel for different tree nodes, further contributing to high peak memory consumption."}

%%%%%%%%%%%%%%%%%%%%%% R8 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{metarevision}
		\textit{Run Scalability experiments with larger datasets.}
	\end{metarevision}
}

\noindent
\textbf{Response:} 
Thank you for your valuable suggestion regarding our experiments. In Section 4.2.3 and Section 4.3.3, we have added experiments on the Deep100M dataset. The results show that most algorithms struggle to balance performance with time and space costs on this large-scale dataset. In particular, StitchedVamana performs poorly on Deep100M. The experimental results are shown in Figure~\ref{fig:attribute big dataset} and Figure~\ref{fig:range big dataset}. \textbf{(Please see the "Large-scale Datasets" part of Section 4.2.3 and Section 4.3.3, highlighted in blue in the revised manuscript.)}
%\textbf{(Please refer to the blue highlighted parts in Section 4.2.4 and Section 4.3.4 under Large-scale Datasets.)}

Section 4.2.3:\textcolor{blue}{"As shown in the Figure 11, on the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating good adaptability to large-scale datasets. However, this also comes with significant memory overhead. The clustering-based algorithm Faiss+HQI\_Batch shows moderate performance but has very low memory overhead, which also has certain practical significance. Furthermore, we do not present the results of StitchedVamana and CAPS, as their recall remained consistently low. StitchedVamana sets the search entry point to 0 by default, which makes it prone to getting stuck in local optima when the entry is far from the target region, hindering effective navigation. CAPS, on the other hand, cannot properly run large-scale dataset experiments because its code implementation does not account for such scenarios."}

Section 4.3.3:
\textcolor{blue}{"As shown in the Figure 16, On the deep100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged. However, their high performance is achieved at the cost of extremely high memory consumption (Figure 12d). In contrast, VBASE and Faiss demonstrate moderate performance while consuming significantly less memory."}

\begin{figure}[htbp]
	\centering
	\includegraphics[width=0.95\linewidth]{fig/attribute_legend.pdf}
	\includegraphics[width=\linewidth]{fig/attribute_100M.pdf}
	\caption{Large-Scale Dataset (AF)}
	\label{fig:attribute big dataset}
\end{figure}

\begin{figure}[htbp]
	\centering
	\includegraphics[width=0.95\linewidth]{fig/range_legend.pdf}
	\includegraphics[width=\linewidth]{fig/range_deep100M.pdf}
	\caption{Large-Scale Dataset (RF)}
	\label{fig:range big dataset}
\end{figure}

### 2025-07-31 Revision/response.tex

%For range filtering, please see section 4.3.1.
 %\textbf{(Please refer to the blue highlighted parts in Section 4.3.1 for range filtering.)}
 Section 4.3.1:
\textcolor{blue}{\textit{\textbf{"Peak memory.}}  
	As explained in the attribute filtering analysis, methods with larger index sizes (including the dataset) tend to exhibit higher peak memory consumption. As shown in Figure12c and Figure12d, range filtering also adheres to this pattern.}

	\textcolor{blue}{WinFilter also presents an exception:  its peak memory usage is also affected by the level of parallelism. Although the final index size remains relatively small, the peak memory usage increases significantly during both construction and search. During construction, this is caused by the parallel building of local indices for each tree node, which results in substantial temporary memory usage. Similarly, during search, WinFilter needs to load multiple local indices in parallel for different tree nodes, further contributing to high peak memory consumption."}

%%%%%%%%%%%%%%%%%%%%%% R8 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{metarevision}
		\textit{Run Scalability experiments with larger datasets.}
	\end{metarevision}
}

\noindent
\textbf{Response:} 
Thank you for your valuable suggestion regarding our experiments. In Section 4.2.3 and Section 4.3.3, we have added experiments on the Deep100M dataset. The results show that most algorithms struggle to balance performance with time and space costs on this large-scale dataset. In particular, StitchedVamana performs poorly on Deep100M. \textbf{(Please see the "Large-scale Datasets" part of Section 4.2.3 and Section 4.3.3, highlighted in blue in the revised manuscript.)}
%\textbf{(Please refer to the blue highlighted parts in Section 4.2.4 and Section 4.3.4 under Large-scale Datasets.)}

Section 4.2.3:\textcolor{blue}{"As shown in the figure 11, on the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating good adaptability to large-scale datasets. However, this also comes with significant memory overhead. The clustering-based algorithm Faiss+HQI\_Batch shows moderate performance but has very low memory overhead, which also has certain practical significance. Furthermore, we do not present the results of StitchedVamana and CAPS, as their recall remained consistently low. StitchedVamana sets the search entry point to 0 by default, which makes it prone to getting stuck in local optima when the entry is far from the target region, hindering effective navigation. CAPS, on the other hand, cannot properly run large-scale dataset experiments because its code implementation does not account for such scenarios."}

Section 4.3.3:
\textcolor{blue}{"As shown in the figure 16, On the deep100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged. However, their high performance is achieved at the cost of extremely high memory consumption, as detailed in Figure 12d. Meanwhile, VBASE and Faiss demonstrate moderate performance but significantly lower memory consumption than the top 3 algorithms."}

### 2025-07-31 Revision/response.tex

\textcolor{blue}{
	UNIFY adopts multiple filtering strategies tailored to different query range sizes, avoiding the limitations of a single strategy in specific scenarios. It requires only one index to support all queries, allows dynamic insertions, and features low time and space overhead during index construction, making it a more general-purpose solution."}

Senction 5.1.3:	\textcolor{blue}{"All of the following methods support both attribute filtering and range filtering.}

\textcolor{blue}{
	ACORN demonstrates average overall performance. Among its variants, ACORN-1 shows significant advantages in indexing speed on 100M-scale datasets, but suffers from high memory consumption and delivers only moderate performance.}

\textcolor{blue}{
	Faiss, Milvus and VBASE effectively handle complex filtering by employing versatile "pre-filtering" or "post-filtering" strategies, granting them significant flexibility and broad applicability. This flexibility, however, is often counterbalanced by their relatively modest overall search performance. Relatively speaking, PASE performs less well across various aspects, which indicates that its strategy of loading data pages on-demand is unsuitable for performance-demanding scenarios."}
%下面放那个优劣势表

@@

%%%%%%%%%%%%%%%%%%%%%% R10 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{metarevision}
		\textit{Clearer guidelines in the Discussion to the extend of recommendations on which system/algo to use for what dataset characteristics.}
	\end{metarevision}
}

\noindent
\textbf{Response:} Thank you very much for your valuable suggestions. Your advice is very insightful. In the recommendation section of our paper, we have added a clearer summary table of the algorithms to help readers choose the appropriate algorithm based on their application scenarios, as shown in Table~\ref{tab:algorithm_recommendation}. \textbf{(Please see Section 5.1, highlighted in blue in the revised manuscript.)}

\textcolor{blue}{"Based on the performance of algorithms across various experimental settings, we evaluate their strengths and weaknesses in different application scenarios, as shown in Table 1. "}

### 2025-07-31 Revision/response.tex

\textcolor{blue}{
	UNIFY adopts multiple filtering strategies tailored to different query range sizes, avoiding the limitations of a single strategy in specific scenarios. It requires only one index to support all queries, allows dynamic insertions, and features low time and space overhead during index construction, making it a more general-purpose solution."}

Senction 5.1.3:	\textcolor{blue}{"All of the following methods support both attribute filtering and range filtering.}

\textcolor{blue}{
	ACORN demonstrates average overall performance. Among its variants, ACORN-1 shows significant advantages in indexing speed on 100M-scale datasets, but suffers from high memory consumption and delivers only moderate performance.}

\textcolor{blue}{
	Faiss, Milvus and VBASE effectively handle complex filtering by employing versatile "pre-filtering" or "post-filtering" strategies, granting them significant flexibility and broad applicability. This flexibility, however, is often counterbalanced by their relatively modest overall search performance. Relatively speaking, PASE performs less well across various aspects."}
%下面放那个优劣势表

@@

%%%%%%%%%%%%%%%%%%%%%% R10 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{metarevision}
		\textit{Clearer guidelines in the Discussion to the extend of recommendations on which system/algo to use for what dataset characteristics.}
	\end{metarevision}
}

\noindent
\textbf{Response:} Thank you very much for your valuable suggestions. Your advice is very insightful. In the recommendation section of our paper, we have added a clearer summary table of the algorithms to help readers choose the appropriate algorithm based on their application scenarios, as shown in Table~\ref{tab:algorithm_recommendation}. \textbf{(Please see Section 5.1.1 and Section 5.1.2, highlighted in blue in the revised manuscript.)}

@@

\end{table*}

\section*{Response to Review 1}

%%%%%%%%%%%%%%%%%%%%%% W1 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{weakness}
		\textit{Although the authors justify the synthetic attribute generation, real-world applications may involve more complex attribute semantics and correlations, which might affect generalizability.}
	\end{weakness}
}

\noindent
\textbf{Response:} I really appreciate your suggestion. Current hybrid query algorithms do not explicitly model or leverage complex semantic relationships, such as those between vectors and their attributes, or among different attributes. Our evaluation covered a range of realistic scenarios, including multi-attribute setting, diverse distributions and selectivity, to assess the algorithms' generalization capabilities (though we used synthetic attributes).

To demonstrate that the choice between synthetic and real attributes has little impact on algorithm performance, we have conducted an additional set of experiments. We used the YouTube-Audio dataset for vectors and compared results with both synthetic and real attributes (video classification). As shown in Figure~\ref{fig:compare}, the experimental outcomes have validated our hypothesis that the impact of using synthetic versus real attributes on the algorithms is limited.

@@

%%%%%%%%%%%%%%%%%%%%%% D3 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{detailed}
		\textit{The paper lists AF algos (table 1) and RF algos (table 2). It would be good to list the systems in a table with their algos and capabilities (AF, RF, Graph, IVF, ...). Would make it easier to follow the experimental comparison. E.g., Fig 12 does not include Vamana/DiskANN. Should I assume that RF is not possible with Vamana, or just not implemented?}
	\end{detailed}
}

\noindent
\textbf{Response:} 
Thank you for the suggestion. We realized that the original wording is somewhat vague and led to confusion among readers. To address this, we merged the tables for attribute filtering (AF) and range filtering (RF), and clarified the support of each algorithm for AF and RF in the unified table, as shown in Table~\ref{tab:compair_1}. For the examples you mentioned—FilteredVamana and StitchedVamana—their original implementations do not support range filtering. Therefore, we mark "N" in the RF (Range Filtering) column of the table. You can refer to the table to see whether each algorithm supports attribute filtering (AF) and range filtering (RF).

	\renewcommand{\arraystretch}{0.9}
\begin{table*}[t]
	\centering
	%\setlength{\belowcaptionskip}{-0.3cm}

	\caption{Comparison of AF-ANN and RF-ANN Search Algorithms}
	\small
	%		\label{tab:compair_1}
	%		\begin{tabular}{|l|l|c|c|c|c|c|c|c|}
		%			\hline
		%			\textbf{Algorithm} & \textbf{Base} & \textbf{Filter Type} & \textbf{AND} & \textbf{OR} & \textbf{Flexible Attributes} & \textbf{Complex Boolean} & \textbf{Dynamic Insert} & \textbf{Multi Thread} \\
		%			\hline
		%			NHQ & Graph & C & Y & N& N& N & N & N \\
		%			FilteredVamana & Graph & C & N & Y & Y & N & Y & Y \\
		%			StitchedVamana & Graph & C & N & Y & Y & N & N & Y  \\
		%			CAPS & IVF & C & Y & N & Y & N & Y & Y \\
		%			ACORN & Graph & B & Y & Y & Y & Y & Y & Y \\
		%			UNG & Graph & B & Y & Y & Y & N & Y & Y \\ 
		%			Puck & IVF & B & Y & Y & Y & N & Y & Y \\
		%			% ParlayANN & Graph+IVF & B & N & N & Y & N & N & Y \\
		%			
		%			\hline
		%			
		%		\end{tabular}
	\label{tab:compair_1}
	\begin{tabular}{|l|l|*{12}{c|}}
		\hline

		\multicolumn{2}{|c|}{\textbf{Characteristics/Algorithms}} & \textbf{NHQ} & \textbf{Filtered} & \textbf{Stitched} & \textbf{CAPS} & \textbf{ACORN} & \textbf{UNG} & \textbf{Puck} & \textbf{DSG} & \textbf{iRange} & \textbf{SeRF} & \textbf{UNIFY} & \textbf{Win}
		\\ \hline
		\multirow{6}{*}{\textbf{AF}} 
		%& Filter Type         & C   & C   & C   & C   & B   & B   & B   & \multicolumn{5}{c|}{} \\ \cline{2-9}
		& AND                 & Y   & N   & N   & Y   & Y   & Y   & Y   & \multicolumn{5}{c|}{\multirow{4}{*}{\centering\shortstack{AF\\Not Support}}} \\ \cline{2-9}
		& OR                  & N   & Y   & Y   & N   & Y   & Y   & Y   & \multicolumn{5}{c|}{} \\ \cline{2-9}
		& Flexible Attributes & N   & Y   & Y   & Y   & Y   & Y   & Y   & \multicolumn{5}{c|}{} \\ \cline{2-9}
		& Complex Boolean     & N   & N   & N   & N   & Y   & N   & N   & \multicolumn{5}{c|}{} \\ \hline

@@

		\multicolumn{2}{|l|}{\textbf{RF}}             & N & N & N & N & Y & N & N & Y & Y & Y & Y & Y \\ \hline
		\multicolumn{2}{|l|}{\textbf{Filter Type }}             & C & C & C & C & B & B & B & B & B & B & A/B/C & A \\ \hline
		\multicolumn{2}{|l|}{\textbf{Dynamic Insert}} & N & Y & N & Y & Y & Y & Y & N & Y & Y & Y & Y \\ \hline
		\multicolumn{2}{|l|}{\textbf{Multi Thread}}   & N & Y & Y & Y & Y & Y & Y & N & Y & Y & Y & Y \\ \hline
		\multicolumn{2}{|l|}{\textbf{Disk Support}}           &N  & Y& N & N & N & N & N & N & N & N & N & N \\ \hline
		\multicolumn{2}{|l|}{\textbf{Base}}           & Graph & Graph & Graph & IVF & Graph & Graph & IVF & Graph & Graph & Graph & Graph & Graph \\ \hline
	\end{tabular}

	%		\begin{tabular}{|c|c|c|c|}
		%			\hline
		%			\textbf{Algorithm} & \textbf{Base} & \textbf{Dynamic Insert} & \textbf{Multi Thread} \\
		%			\hline
		%			DSG & Graph & Y & N \\
		%			iRange & Graph & N & Y \\
		%			SeRF & Graph & Y & Y \\
		%			UNIFY & Graph & Y & Y \\
		%			WinFilter & Graph & N & Y  \\
		%			\hline
		%		\end{tabular}
	%

	\centering
	%	 \setlength{\abovecaptionskip}{0cm}
	%	\setlength{\belowcaptionskip}{0.1cm}
	\footnotesize{
		\begin{minipage}{\linewidth}
			\vspace{0.1cm}
			Win: WinFilter, Filtered: FilteredVamana, Stitched: StitchedVamana. 
			\textsuperscript{A} Post-filtering, 
			\textsuperscript{B} Pre-filtering, 
			\textsuperscript{C} Simultaneous filtering, 
			\textsuperscript{Y} Support, 
			\textsuperscript{N} Unsupport. 
			\textit{AND} and \textit{OR} indicate whether the algorithm supports the corresponding logical operations.
			\textit{Flexible Attributes} indicates whether the number of query attributes can differ from the number of attributes used during index construction. 
			\textit{Complex Boolean} indicates if the algorithm supports complex expressions, such as using the NOT operator or nested logic with parentheses.
			\textit{Dynamic Insert} indicates whether the algorithm supports the operation of dynamically inserting data points.
			\textit{Multi Thread} indicates whether the algorithm supports multi-threaded search.
			\textit{Disk Support} indicates whether the algorithm supports disk storage.
			\textit{Base} indicates the foundational ANN algorithm for the hybrid query method.
	\end{minipage}}

### 2025-07-31 Revision/response.tex

\textcolor{blue}{
	Faiss, Milvus and VBASE effectively handle complex filtering by employing versatile "pre-filtering" or "post-filtering" strategies, granting them significant flexibility and broad applicability. This flexibility, however, is often counterbalanced by their relatively modest overall search performance. Relatively speaking, PASE performs less well across various aspects."}
%下面放那个优劣势表

%%%%%%%%%%%%%%%%%%%%%% R10 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{metarevision}
		\textit{Clearer guidelines in the Discussion to the extend of recommendations on which system/algo to use for what dataset characteristics.}
	\end{metarevision}
}

\noindent
\textbf{Response:} Thank you very much for your valuable suggestions. Your advice is very insightful. In the recommendation section of our paper, we have added a clearer summary table of the algorithms to help readers choose the appropriate algorithm based on their application scenarios, as shown in Table~\ref{tab:algorithm_recommendation}. \textbf{(Please see Section 5.1, highlighted in blue in the revised manuscript.)}

\textcolor{blue}{"Based on the performance of algorithms across various experimental settings, we evaluate their strengths and weaknesses in different application scenarios, as shown in Table \ref{tab:algorithm_recommendation}. "}

@@

\textcolor{blue}{"Let \( D = \{(v_1, a_1), \ldots, (v_n, a_n)\} \) be a dataset of \( n \) \( d \)-dimensional vectors, each associated with an attribute value \( a_i \)."}

%%%%%%%%%%%%%%%%%%%%%% D4 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{detailed}
		\textit{ In Section 4.1, please clarify the URL of the implementation of each method.}
	\end{detailed}
}

\noindent
\textbf{Response:} 
Thank you for the suggestion. Since there are multiple methods, listing all URLs in Section 4.1 would be overwhelming. Instead, in Section 3, we added superscript markers next to each algorithm name and provided the corresponding implementation URLs as footnotes on the same page. \textbf{(Please see Section 3, highlighted in blue in the revised manuscript.)}

%\textcolor{blue}{"https://github.com/KGLab-HDU/TKDE-under-review-Native-Hybrid-Queries-via-ANNS"}
%
%\textcolor{blue}{"https://github.com/microsoft/DiskANN"}
%
%\textcolor{blue}{"https://github.com/gaurav16gupta/constrainedANN"}
%
%\textcolor{blue}{"https://github.com/stanford-futuredata/ACORN"}
%
%\textcolor{blue}{"https://github.com/YZ-Cai/Unified-Navigating-Graph"}
%
%\textcolor{blue}{"https://github.com/baidu/puck"}
%
%\textcolor{blue}{"https://github.com/rutgers-db/SeRF"}
%
%\textcolor{blue}{"https://github.com/JoshEngels/RangeFilteredANN"}
%
%\textcolor{blue}{"https://github.com/YuexuanXu7/iRangeGraph"}
%
%\textcolor{blue}{"https://github.com/rutgers-db/DynamicSegmentGraph"}
%
%\textcolor{blue}{"https://github.com/sjtu-dbgroup/UNIFY"}
%
%\textcolor{blue}{"https://github.com/facebookresearch/faiss"}
%
%\textcolor{blue}{"https://github.com/alipay/PASE"}
%
%\textcolor{blue}{"https://github.com/microsoft/MSVBASE"}
%
%\textcolor{blue}{"https://github.com/milvus-io/milvus"}

@@

\section*{Response to Review 3}
\setcounter{weakness}{0}

%%%%%%%%%%%%%%%%%%%%%% W1 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{weakness}
		\textit{Scalability experiments are missing; largest dataset is 10M; some pitfalls will only show at large scale.}
	\end{weakness}
}

\noindent
\textbf{Response:} 
Thank you for your suggestion. We have added experiments on the Deep100M dataset in Section 4.2.3 and Section 4.3.3. For more details, please refer to our response to Meta R7.

### 2025-07-31 Revision/response.tex

\noindent
\textbf{Response:} 
We believe your suggestion is very reasonable, and the experiment on search peak memory is indeed an important component. We are deeply aware of this shortcoming, so we provide the search peak memory usage of each algorithm in the time and space overhead section and carefully analyze the reasons. For more details, please refer to our response Meta R6.

%We have made a detailed response to this issue in our reply to Meta R6. Please refer to that response for more information.

%%%%%%%%%%%%%%%%%%%%%% D1 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{detailed}
		\textit{The authors have cited an experimental paper [49],
			but have not discussed about the main difference between their paper and [49].}
	\end{detailed}
}

\noindent
\textbf{Response:} 
%Thank you for pointing this out. Both paper [49] and our paper are benchmarks. Paper [49] provides a comprehensive review and evaluation of graph-based approximate nearest neighbor search algorithms. Our paper is the first benchmark to evaluate hybrid queries. Since hybrid queries are developed based on ANN, we refer to the evaluation metrics proposed in the cited paper. We realize that we did not clearly explain the difference between our paper and the cited paper, so we have added a description in the introduction, please see section 1.1.
Thank you for pointing this out. The original reference [49](now [50] in our latest version), provides a comprehensive review and evaluation of graph-based approximate nearest neighbor (ANN) search algorithms, whereas our work is the first to establish a benchmark specifically for hybrid query algorithms. We initially cited this reference in the experimental setup section to adopt its proposed evaluation metrics, as hybrid queries are fundamentally built upon ANN techniques. We acknowledge that the distinction between our work and the cited paper was not clearly articulated in the early version. To address this, we have revised the introduction to clarify the difference and added citations to several experimental studies from the ANN literature. \textbf{(Please see Section 1.1, highlighted in blue in the revised manuscript.)}

 \textcolor{blue}{
% 	Although existing work, such as the survey [49] by reviews graph-based ANN methods, the literature still lacks an experimental study specifically targeting hybrid query algorithms. To address this gap, we conduct the first comprehensive experimental evaluation of hybrid query algorithms, systematically analyzing their index construction costs and query efficiency across diverse scenarios. Furthermore, we rigorously assess the robustness of each algorithm under varying conditions, thereby providing valuable insights for future research and practical applications.
 	"Although existing works [9,45] conduct benchmark evaluations of ANN methods, a systematic experimental study specifically targeting hybrid query algorithms is still lacking."}

@@

%%%%%%%%%%%%%%%%%%%%%% D2 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{detailed}
		\textit{In Section 1.1, I could not find convincing references for the requirements in practical applications.
			[12] and [36] are research papers only, but not from real applications.}
	\end{detailed}
}

\noindent
 \textbf{Response:} 
 Thank you for your suggestion. We cited these two papers in the introduction to show that there are several papers that study attribute distribution and selectivity.
% In addition, attribute distribution and selectivity are indeed widely used in real-world scenarios. For attribute distribution, the label attributes of many recommendation application scenarios in reality conform to the power-law distribution. For attribute selectivity: for example, if you need to query data with a very small proportion of a certain attribute, choosing a better algorithm will greatly improve the search effect. 
There are also some databases with practical applications that mention attribute selectivity, such as Milvus and AnalyticDB-V. Therefore, we have replaced them in the paper with more comprehensive and accurate references. \textbf{(Please see Section 1.1, highlighted in blue in the revised manuscript.)}
\textcolor{blue}{"For attribute filtering algorithms, factors such as the number of attributes, attribute distribution [13], and attribute selectivity [42,47] significantly impact algorithm performance."}

### 2025-07-31 Revision/response.tex

\noindent
\textbf{Response:} 
Thank you for your valuable suggestion regarding our experiments. In Section 4.2.3 and Section 4.3.3, we have added experiments on the Deep100M dataset. The results show that most algorithms struggle to balance performance with time and space costs on this large-scale dataset. In particular, StitchedVamana performs poorly on Deep100M. The experimental results are shown in Figure~\ref{fig:attribute big dataset} and Figure~\ref{fig:range big dataset}. \textbf{(Please see the "Large-scale Datasets" part of Section 4.2.3 and Section 4.3.3, highlighted in blue in the revised manuscript.)}
%\textbf{(Please refer to the blue highlighted parts in Section 4.2.4 and Section 4.3.4 under Large-scale Datasets.)}

Section 4.2.3:\textcolor{blue}{"As shown in the Figure 11, on the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating good adaptability to large-scale datasets. However, this also comes with significant memory overhead. The clustering-based algorithm Faiss+HQI\_Batch shows moderate performance but has very low memory overhead, which also has certain practical significance. Furthermore, we do not present the results of StitchedVamana and CAPS, as their recall remained consistently low. StitchedVamana sets the search entry point to 0 by default, which makes it prone to getting stuck in local optima when the entry is far from the target region, hindering effective navigation. CAPS, on the other hand, cannot properly run large-scale dataset experiments because its code implementation does not account for such scenarios."}

Section 4.3.3:
\textcolor{blue}{"As shown in the Figure 16, On the deep100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged. However, their high performance is achieved at the cost of extremely high memory consumption (Figure 12d). In contrast, VBASE and Faiss demonstrate moderate performance while consuming significantly less memory."}

\begin{figure}[htbp]
	\centering
	\includegraphics[width=0.95\linewidth]{fig/attribute_legend.pdf}
	\includegraphics[width=0.7\linewidth]{fig/attribute_100M.pdf}
	\caption{Large-Scale Dataset (AF)}
	\label{fig:attribute big dataset}
\end{figure}

\begin{figure}[htbp]
	\centering
	\includegraphics[width=0.95\linewidth]{fig/range_legend.pdf}
	\includegraphics[width=0.7\linewidth]{fig/range_deep100M.pdf}
	\caption{Large-Scale Dataset (RF)}
	\label{fig:range big dataset}
\end{figure}
